---
title: "Weather forecast API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Weather forecast API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Weather forecast data for five large cities in Sweden. Could be used with a shiny application.
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Weather4cats)
```
## The input
To use the function, a city and a date must be inputted.

### City
The city has start with a uppercase letter. The valid cities are:

* Stockholm
* Göteborg
* Mölmö
* Uppsala
* Linköping

### Date
The date has to be encoded as "YYYY-MM-DD" and could be between today and seven days ahead.

## The output
The output is a data.frame with 24 rows and 8 columns containing hourly information for the following variables:

* Time (every hour of the requested day)
* Temperature (Degrees Celsius)
* Humidity (%)
* Precipitation (millimeter)
* Cloudcover (%)
* Wind speed (meter/second)
* Wind direction (degrees)
* City (from input)

## Example
```{r}
# Requesting the weather forecast for Uppsala, today.
# Call:
example <- get_weather_forecast(city="Uppsala", date=Sys.Date())

# Structure
str(example)

# First three rows
print(head(example, 3))

# Last tree rows of example
print(tail(example, 3))

# Short summary
summary(example)

```

